---
title: "Grid vs Cell registration"
author: "Michael Sumner, Ben Raymond"
date: "July 27, 2015"
output: html_document
---

Grids can be registered in one of two ways: 

* grid (or node) registration
* cell registration. 

Sometimes the distinction doesn't matter, but ...

The Etopo1 global topography data set is delivered in either cell or grid, bu


# Law dome

```{r}
etopo1home <- "D:/data/topography/Etopo1"
library(raster)
grid <- raster(file.path(etopo1home, "ETOPO1_Ice_g_geotiff.tif"))
cell <- raster(file.path(etopo1home, "ETOPO1_Ice_c_geotiff.tif"))
pt <- rev(c(-66.733333, 112.833333))
ext <- extent(c(matrix(pt + c(-1, -1, 1, 1) * c(0.5, 0.4), byrow = TRUE, ncol = 2)))

plot(crop(grid, ext, snap = "out"), col = palr::sstPal(50), asp = 1)
```

Convert to rgl format and plot. 

```{r}
library(rgl)
library(gris)
if(FALSE) {
  rgl.pop()
}

sfact <- 5e3
ggl <- bgl(crop(grid, ext, snap = "out"), crop(grid, ext, snap = "out")/sfact)
scl <- function(x) (x - min(x))/diff(range(x))
shade3d(ggl, col = rep(palr::sstPal(256)[scl(values(crop(grid, ext, snap = "out"))) * 255 + 1], each = 4))
cgl <- bgl(crop(cell, ext, snap = "out"), crop(cell, ext, snap = "out")/sfact)
shade3d(cgl, col = rep(palr::sstPal(256)[scl(values(crop(grid, ext, snap = "out"))) * 255 + 1], each = 4))

gpts <- rasterToPoints(crop(grid, ext, snap = "out")/sfact)
rgl.points(gpts[,1], gpts[,2], gpts[,3], col = "black")
gpts <- gris(rasterToPoints(crop(grid, ext, snap = "out"), spatial = TRUE))
gpoly <- gris(rasterToPolygons(crop(grid, ext, snap = "out")))
pslgpoly <- mkpslg(gpoly)
with(pslgpoly, apply(S[1:4, ], 1, function(x) rgl.lines(P[x, ])))
ps <- pslg(P = as.matrix(gpts$v[, c("x", "y")]))

 allv <- gpoly$bXv  %>% inner_join(gpoly$v, c(".vx0" = ".vx0"))  %>% inner_join(gpoly$b)  %>% inner_join(gpoly$oXb)  %>% inner_join(gpoly$o)
 
 for (j in unique(allv$.ob0)) {
   with(filter(allv, .ob0 == j), rgl.quads(x, y, ETOPO1_Ice_g_geotiff/2e3))
   }
 
rgl.points(gpts$o$x, gpts$o$y, gpts$o$ETOPO1_Ice_g_geotiff/2e3, col = "black")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
