---
title: "Ocean colour L2"
author: "Michael Sumner"
date: "14 June 2015"
output: html_document
---

Get a L2 ocean colour file. 

```{r,eval=FALSE}
f <- "http://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A2015034000000.L2_LAC_OC.bz2"
dp <- "/rdsi/PRIVATE/dev/"

ff <- file.path(dp, basename(f))
if (!file.exists(ff)) download.file(f, ff, mode = "wb")
if (grepl("bz2", basename(ff))) {
  system(sprintf("bunzip2 -k %s", basename(ff)))
  ff <- gsub(".bz2$", "", ff)
}
library(raster)
#rlon <- raster(ff, varname = "navigation_data/longitude")
#rlat <- raster(ff, varname = "navigation_data/latitude")
#r <- raster(ff, varname = "geophysical_data/chlor_a")
rlon <- raster('HDF4_SDS:UNKNOWN:"/rdsi/PRIVATE/dev//A2015034000000.L2_LAC_OC":11')
rlat <- raster('HDF4_SDS:UNKNOWN:"/rdsi/PRIVATE/dev//A2015034000000.L2_LAC_OC":12')
r <- raster('HDF4_SDS:UNKNOWN:"/rdsi/PRIVATE/dev//A2015034000000.L2_LAC_OC":27')
library(dplyr)
x <- data_frame(x = values(rlon), y = values(rlat), chl = values(r))
##save(x, file = gsub("nc$", "RData", basename(ff)))
save(x, file = paste0(basename(ff), "RData"))
```

```{r}
library(dplyr)
library(palr)
load("E:/DATA/NASA/A2015034000000.L2_LAC_OC.RData")
x %>% summarize(min(chl, na.rm = TRUE))
x1 <- x %>% filter(chl > 0) 

## something something something . . .
#   exy <- edgesXY(x)
#   ind <- apply(prs(seq(ncol(x) + 1)), 1, p4, nc = ncol(x) + 1)
#   ## all face indexes
#   ind0 <- as.vector(ind) + 
#     rep(seq(0, length = nrow(x), by = ncol(x) + 1), each = 4 * ncol(x))
#   
# with(x1, plot(x, y, col = chlPal(chl), pch = "."))
# dm <-  c(2030, 1354)#c(768, 3200)
# 
# image(setValues(raster(nrow = dm[1], ncol = dm[2]), x$chl), useRaster = TRUE, col = palr::chlPal(100))
# 
# 
# plot(sort(x$chl), pch = ".")
